The Sub-Millimetre User Reduction Facility: an iterative map-maker for SCUBA-2

### 2012-04-02 smurf_paper.tex
small test commit from behind ESAC firewall

The first step, map generation, is different from that described in
Section~\ref{sec:point} in two key ways. Since the locations of
sources are unknown \emph{a priori}, a map constraint is not
employed. Large-scale diverging structures in the map must be
mitigated, and the method used in this example (the default processing
in SMURF) is to apply a high-pass filter to the data \emph{once} as a
pre-processing steps. The iterative solution is then run using only
\model{COM}, \model{EXT}, \model{AST}, and \model{NOI}. In other
words, there is no information in the bolometer signals below some
cutoff frequency, and residual noise is removed only using iterative
estimation of the residual (higher-frequency) common-mode. The map is
shown in Fig.~\ref{fig:lockman_maps}a. The map-maker has been tested
in two ways: (i) large numbers of iterations are used to verify that
the maps converge without the growth of large structure; and (ii)
adding synthetic sources to the data at a range of brightnesses verify
that the map-maker response to them is \emph{linear} (i.e. the
relative shape and amplitude compared to the input source is
independent of brightness). The results of this second test are shown
by the solid and dotted lines in Fig.~\ref{fig:lockman_psf},
respectively. Clearly the down-side of using a high-pass filter as a
pre-processing step, and having no other map-constraints, has the
down-side of introducing sidelobes around the main peak. ... high-pass
filter + iterative common-mode removal takes place of PCA cleaning in
AzTEC reduction ... probably more linear.

>>>>

The first step, map generation, is different from that described in
Section~\ref{sec:point} in two key ways. Since the locations of
sources are unknown \emph{a priori}, a map constraint is not
employed. Large-scale diverging structures in the map must be
mitigated, and the method used in this example (the default processing
in SMURF) is to apply a high-pass filter to the data \emph{once} as a
pre-processing steps. The iterative solution is then run using only
\model{COM}, \model{EXT}, \model{AST}, and \model{NOI}. In other
words, there is no information in the bolometer signals below some
cutoff frequency, and residual noise is removed only using iterative
estimation of the residual (higher-frequency) common-mode. The map is
shown in Fig.~\ref{fig:lockman_maps}a. The map-maker has been tested
in two ways: (i) large numbers of iterations are used to verify that
the maps converge without the growth of large structure; and (ii)
adding synthetic sources to the data at a range of brightnesses verify
that the map-maker response to them is \emph{linear} (i.e. the
relative shape and amplitude compared to the input source is
independent of brightness). The results of this second test are shown
by the solid and dotted lines in Fig.~\ref{fig:lockman_psf},
respectively. Clearly the use of a high-pass filter as a
pre-processing step, and having no other map-constraints, has the
down-side of introducing sidelobes around the main peak. However, the
way this filter affects point-sources is both well-known, and linear.

%... high-pass
%filter + iterative common-mode removal takes place of PCA cleaning in
%AzTEC reduction ... probably more linear.
